|

### 2022-06-14 draft-1.Rmd
Update draft-1.Rmd

```{r tab.id = "sarlm", tab.cap = "Spatial lag regression coefficients for each mental health outcome"}
sarlm_tab <- model_list %>%
  map(function(x) {
    extract.Sarlm2(x)
  }) %>%
  texreg::matrixreg(
    single.row = T,
    booktabs = T,
    dcolumn = T,
    custom.model.names = c("MHLTH", "DEPRESSION", "SLEEP"),
    custom.coef.names = c(
      "(Intercept)",
      "Mean NDVI",
      "Greenspace Area",
      "Percent White",
      "Income",
      "Amenities",
      "Trails",
      "rho"
    ),
    float.pos = "h"
  ) %>% 
  as.data.frame() %>% 
  as_tibble() %>% 
  `colnames<-`(.[1, ]) %>% 
  .[-1, ]
sarlm_tab
```

>>>>

```{r tab.id = "sarlm", tab.cap = "Spatial lag regression coefficients for each mental health outcome"}
sarlm_tab <- model_list %>%
  map(function(x) {
    extract.Sarlm2(x)
  }) %>%
  texreg::matrixreg(
    single.row = T,
    booktabs = T,
    dcolumn = T,
    custom.model.names = c("MHLTH", "DEPRESSION", "SLEEP"),
    custom.coef.names = c(
      "(Intercept)",
      "Mean NDVI",
      "Greenspace Area",
      "Percent White",
      "Income",
      "Amenities",
      "Trails",
      "rho"
    ),
    float.pos = "h"
  ) %>% 
  as.data.frame() %>% 
  tibble::as_tibble() %>% 
  `colnames<-`(.[1, ]) %>% 
  .[-1, ] %>% 
  `colnames<-`(c("Variable", "MHLTH", "DEPRESSION", "SLEEP"))
sarlm_tab
```
